---
title: "Lists"
---

```{r setup}
library(tidyverse)
library(repurrrsive)
library(broom)
names(sw_people) <- sw_people %>% map_chr("name")
```

# Lists

## Your Turn 1

Run the code below, which displays a list. What do you see? #comment the code to indicate what each code line does.

```{r}
sw_people %>% head(3) #prints the first 3 characters from the list
sw_people$`Luke Skywalker` #print Luke Skywalker
sw_people[[2]] #Print C-3PO
```


```{r}
l_1 <- list(x = c(1,2,3), y = "two", z = FALSE)

l_1$x
```

## Quiz
What does `abs()` do for vectors vs. lists?


```{r}
vec <- c(-2, -1, 0)
lst <- list(-2, -1, 0)

abs(vec)
#abs(lst)
```



## Your Turn 2

Who was taller Anakin Skywalker or Darth Vader? 
Use the RStudio Viewer to find the answer (in cm).
Extract the code to answer the question and copy/paste it here

*Hint: View() sw_people*

```{r}
#View(sw_people)

#Darth Vader is taller (202cm vs 188cm)
```

## Your Turn 3

Here are two subsetting commands. Do they return the same values? Run the code chunks below to confirm. #comment the code to indicate what each chunk does

```{r}
a_list <- list(num = c(8, 9), 
               log = TRUE,    
               cha = c("a", "b", "c"))
```

```{r}
a_list["num"] #Prints the "num" vector in the list plus the vector name
```

```{r}
a_list[["num"]] #Prints the "num" vector in the list
```


Take Aways

* Use `View()` to inspect lists
* Use `[[ ]]`, or `$` to extract values from lists
* Lists can be a column in a data frame
* Tables are an organizational structure that you can manipulate.
